Approximation as Differentiation

### 2025-06-09 main/first-order.tex
Tweaks to CMon categories.

For differentiable functions, we can combine linear approximations by adding tangent vectors; for stable
functions, we can combine approximants by taking their meet. In both cases the additive structure is given by
a commutative monoid with addition + and zero element 0. A category $\cat{C}$ is enriched in $\CMon$, the
(monoidal) category of commutative monoids, when every hom-set $\cat{C}(X,Y)$ provides an operation + to add
morphisms together plus a zero morphism $0: X \to Y$, and composition is \emph{bilinear}, i.e.~given by a
family of morphisms $\Hom{\cat{C}}{Y}{Z} \tensor \Hom{\cat{C}}{X}{Y} \to \Hom{\cat{C}}{X}{Z}$ in $\CMon$ that
preserve the additive structure in $\Hom{\cat{C}}{Y}{Z}$ and $\Hom{\cat{C}}{X}{Y}$ separately:

@@

@@

In any $\CMon$-category, any products and coproducts coincide.

\begin{proposition}
\label{prop:biproducts:from-product-or-coproduct}
In any $\CMon$-category:
\begin{enumerate}
\item If $X \times Y$ is a product then it is also coproduct, with $\inj_X = \prodM{\id_X}{0_{X,Y}}$ and
$\inj_Y = \prodM{0_{X,Y}}{\id_Y}$.
\item If $X \coprod Y$ is a coproduct then it is also a product, with $\pi_1 = \coprodM{\id_X}{0_{Y,X}}$ and
$\pi_2 = \coprodM{0_{X,Y}}{\id_Y}$.
\item $X$ is terminal iff $X$ is initial.
\end{enumerate}
\end{proposition}

An object that is both terminal and initial is called a \emph{zero} object; an object that is both a product
and a coproduct is called a \emph{biproduct}. More directly, a biproduct is as an object $X \biprod Y$
together with morphisms

>>>>

\subsubsection{$\CMon$-Categories}

To say that a category $\cat{C}$ is enriched in $\CMon$, the (monoidal) category of commutative monoids, is to
say that every hom-set $\cat{C}(X,Y)$ provides an operation + to add morphisms together plus a zero morphism
$0: X \to Y$, and moreover that composition is \emph{bilinear}, i.e.~given by a family of morphisms
$\Hom{\cat{C}}{Y}{Z} \tensor \Hom{\cat{C}}{X}{Y} \to \Hom{\cat{C}}{X}{Z}$ in $\CMon$ that preserve the
additive structure in $\Hom{\cat{C}}{Y}{Z}$ and $\Hom{\cat{C}}{X}{Y}$ separately:

@@

In a $\CMon$-category, any products and coproducts coincide.

\begin{proposition}
\label{prop:biproducts:from-product-or-coproduct}
In any $\CMon$-category:
\begin{enumerate}
\item If $X \times Y$ is a product then it is also coproduct, with $\inj_X = \prodM{\id}{0}$ and $\inj_Y =
\prodM{0}{\id}$.
\item If $X \coprod Y$ is a coproduct then it is also a product, with $\pi_1 = \coprodM{\id}{0}$ and $\pi_2 =
\coprodM{0}{\id}$.
\item $X$ is terminal iff it is initial.
\end{enumerate}
\end{proposition}

An object that is both terminal and initial is called a \emph{zero} object; an object that is both a product
and a coproduct is called a \emph{biproduct}.

@@

More directly, a biproduct is as an object $X \biprod Y$ together with morphisms
